### 2024-07-20 mythbusters.qmd
20240720 - effect sizes

```{r}
library("petersenlab")
library("lme4")
library("lmerTest")
library("tidyverse")
```

@@

@@

# Calculate Per Game Totals
nfl_actualStatsContracts_seasonal <- nfl_actualStatsContractsSubset_offense_weekly %>% 
  dplyr::group_by(playerMerge, season) %>% 
  dplyr::summarise(
    position_group = petersenlab::Mode(position_group),
    rushing_yards = sum(rushing_yards, na.rm = TRUE), # season total
    carries = sum(carries, na.rm = TRUE), # season total
    rushing_epa = mean(rushing_epa, na.rm = TRUE),
    receiving_yards = mean(receiving_yards, na.rm = TRUE),
    receiving_epa = mean(receiving_epa, na.rm = TRUE),
    contractYear = mean(contractYear, na.rm = TRUE),
    games = n(),
    .groups = "drop_last"
  ) %>% 
  dplyr::mutate(ypc = rushing_yards / carries)

@@

nfl_contractYearQBR_weekly$contractYear[which(is.na(nfl_contractYearQBR_weekly$contractYear))] <- 0

@@

# Calculate Per Game Totals
nfl_contractYearQBR_seasonal <- nfl_contractYearQBRsubset_weekly %>% 
  dplyr::group_by(playerMerge, season) %>% 
  dplyr::summarise(
    qbr = mean(qbr_total, na.rm = TRUE),
    pts_added = mean(pts_added, na.rm = TRUE),
    epa_pass = mean(pass, na.rm = TRUE),
    qb_plays = sum(qb_plays, na.rm = TRUE), # season total
    contractYear = mean(contractYear, na.rm = TRUE),
    games = n(),
    .groups = "drop_last"
  )

@@

summary(mixedModel_qbr)
```

@@

summary(mixedModel_ptsAdded)
```

@@

summary(mixedModel_epaPass)
```

@@

summary(mixedModel_ypc)
```

@@

summary(mixedModel_epaRush)
```

@@

summary(mixedModel_receivingYards)
```

@@

summary(mixedModel_epaReceiving)
```

>>>>

```{r}
library("petersenlab")
library("lme4")
library("lmerTest")
library("MuMIn")
library("emmeans")
library("tidyverse")
```

```{r}
#| include: false

emm_options(lmerTest.limit = 100000)
emm_options(pbkrtest.limit = 100000)
```

@@

#nfl_actualStatsContracts_offense_weekly$contractYear <- factor(
#  nfl_actualStatsContracts_offense_weekly$contractYear,
#  levels = c(0, 1),
#  labels = c("no", "yes"))

#nfl_actualStatsContracts_offense_seasonal$contractYear <- factor(
#  nfl_actualStatsContracts_offense_seasonal$contractYear,
#  levels = c(0, 1),
#  labels = c("no", "yes"))

@@

# Calculate Per Game Totals
nfl_actualStatsContracts_seasonal <- nfl_actualStatsContractsSubset_offense_weekly %>% 
  dplyr::group_by(playerMerge, season) %>% 
  dplyr::summarise(
    position_group = petersenlab::Mode(position_group),
    rushing_yards = sum(rushing_yards, na.rm = TRUE), # season total
    carries = sum(carries, na.rm = TRUE), # season total
    rushing_epa = mean(rushing_epa, na.rm = TRUE),
    receiving_yards = mean(receiving_yards, na.rm = TRUE),
    receiving_epa = mean(receiving_epa, na.rm = TRUE),
    contractYear = mean(contractYear, na.rm = TRUE),
    games = n(),
    .groups = "drop_last"
  ) %>% 
  dplyr::mutate(
    ypc = rushing_yards / carries,
    contractYear = factor(
      contractYear,
      levels = c(0, 1),
      labels = c("no", "yes")
    ))

@@

nfl_contractYearQBR_weekly$contractYear[which(is.na(nfl_contractYearQBR_weekly$contractYear))] <- 0
#nfl_contractYearQBR_weekly$contractYear <- factor(
#  nfl_contractYearQBR_weekly$contractYear,
#  levels = c(0, 1),
#  labels = c("no", "yes"))

@@

# Calculate Per Game Totals
nfl_contractYearQBR_seasonal <- nfl_contractYearQBRsubset_weekly %>% 
  dplyr::group_by(playerMerge, season) %>% 
  dplyr::summarise(
    qbr = mean(qbr_total, na.rm = TRUE),
    pts_added = mean(pts_added, na.rm = TRUE),
    epa_pass = mean(pass, na.rm = TRUE),
    qb_plays = sum(qb_plays, na.rm = TRUE), # season total
    contractYear = mean(contractYear, na.rm = TRUE),
    games = n(),
    .groups = "drop_last"
  ) %>% 
  dplyr::mutate(
    contractYear = factor(
      contractYear,
      levels = c(0, 1),
      labels = c("no", "yes")
    ))

@@

summary(mixedModel_qbr)
MuMIn::r.squaredGLMM(mixedModel_qbr)
emmeans::emmeans(mixedModel_qbr, "contractYear")
```

@@

summary(mixedModel_ptsAdded)
MuMIn::r.squaredGLMM(mixedModel_ptsAdded)
emmeans::emmeans(mixedModel_ptsAdded, "contractYear")
```

@@

summary(mixedModel_epaPass)
MuMIn::r.squaredGLMM(mixedModel_epaPass)
emmeans::emmeans(mixedModel_epaPass, "contractYear")
```

@@

summary(mixedModel_ypc)
MuMIn::r.squaredGLMM(mixedModel_ypc)
emmeans::emmeans(mixedModel_ypc, "contractYear")
```

@@

summary(mixedModel_epaRush)
MuMIn::r.squaredGLMM(mixedModel_epaRush)
emmeans::emmeans(mixedModel_epaRush, "contractYear")
```

@@

summary(mixedModel_receivingYards)
MuMIn::r.squaredGLMM(mixedModel_receivingYards)
emmeans::emmeans(mixedModel_receivingYards, "contractYear")
```

@@

summary(mixedModel_epaReceiving)
MuMIn::r.squaredGLMM(mixedModel_epaReceiving)
emmeans::emmeans(mixedModel_epaReceiving, "contractYear")
```
